### 2016-03-14 paper/result_layered_depthmap.tex
minor changes

At the end we examined the role of multi-threading by varying the number of threads N in our most general model SF (See Fig.~\ref{fig:layered_depthmap_by_N})~\footnote{Note that we have the constraint that $\beta \leq N-1$, we always use $\beta = N-1$ in this experiment.}. The plot shows that SF finds low energy faster with more threads. In Fusion Move like methods, parallism speed up convergence by exploring solution proposals faster. While due to the inherited randomness in the proposal generation scheme, the speed up is often not proportional to the number of threads.
%We can see that as the number of
%ways to fuse becomes larger, each fusion step takes longer time, but the
%chance of finding a lower energy state increases.

>>>>

At the end we examined the role of multi-threading by varying the number of threads N in our most general model SF (See Fig.~\ref{fig:layered_depthmap_by_N})~\footnote{While keeping other parameters the same, we have to change $beta$ with $N$ because of the constraint $\beta \leq N-1$. We always use $\beta = N-1$ in this experiment.}. The plot shows that SF finds low energy faster with more threads. In Fusion Move like methods, parallism speed up convergence by exploring solution proposals faster. Due to the inherited randomness in the proposal generation scheme, the speed up is often not proportional to the number of threads.
%We can see that as the number of
%ways to fuse becomes larger, each fusion step takes longer time, but the
%chance of finding a lower energy state increases.
